%!TEX root = ../thesis.tex

\begin{acknowledgements}
Despite the fact that only one name appears on the cover of this work, this thesis was the product of many contributions by many people over many years. Most importantly I would like to thank my advisor, Dr. Sabine Stanley. Your guidance, insight, and support were the primary factor in this thesis being completed. I have often remarked to friends that I had the best advisor in the Department of Physics at the University of Toronto, and I would like to re-iterate that here. You are one of the most intelligent, insightful, and kindest people I have ever met. I am fortunate to have been a student of yours for my doctoral studies.

Thanks to the rest of the Stanley research group and the whole EAPP\footnote{Earth and Planetary Physics, pronounced ``YAPP''} section for your stimulating conversations and expertly feigned interest at one too many Brewer-Wilson (Brewson) seminars.

I would also like to thank my family: Mom, Dad, and Derek. Your unconditional love and support was a great constant during my long tenure as a graduate student. Also, without your constant harassment concerning ``growing up'', ``getting a job'', and ``saving for retirement'' I'm pretty sure I'd be a grad forever. I was living the good life, making \$19,000 a year and living amongst the crack addicts next to Hooker Harveys, who'd want to change that?

Finally I would like to thank my friends, whose support and distractions were instrumental in securing my sanity long enough for this thesis to be eventually completed. In particular I'd like to thank Andrew Lovett-Barron, Niall Ryan, Phil Heron, Keven Roy, Maria Tibbo, Claire Apostoli, Rosie Chapman-Smith, Miranda Begley, Tom Le, and Oliver Watt-Meyer. You kept me from dropping out or becoming an anti-social super-nerd. Cheers.

Of course nobody mentioned in this section will ever know how grateful I am. I'm sure I don't know anyone narcissistic enough to read an acknowledgments section to see if they got a mention, do I?
\end{acknowledgements}